Assessing the Firing of Ceramic Materials: a Seriation-Based Approach

### 2023-06-09 analysis/paper/paper.qmd
Prepare for first release

| **Version** | **Date**   | **Description**            | **DOI** |
|------------:|-----------:|:---------------------------|:--------|
| 0.0.0.9000  |  | Submitted to _Archéosciences_ |  |

>>>>

| **Version** | **Date**   | **Description**            | **DOI** |
|------------:|-----------:|:---------------------------|:--------|
| 1.0.0       | 2023-06-09 | Submitted to _Archéosciences_ |  |
